Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-01-24 awipev-CO2.Rmd
MAintenance updated with frozen samples details

### **FerryBox**
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

@@

### **Durafet**
Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off. This reference point was not takken in consideration for calibration. The window of the previous and next calibration periods was extended.

@@

### **SNAPO**
- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements. Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater. We will ad a lack of DIC for this week. TA will be measured in Villefranche.
- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).

>>>>

### **FerryBox**
- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

@@

### **Durafet**
- Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off. This reference point was not takken in consideration for calibration. The window of the previous and next calibration periods was extended.

@@

### **SNAPO**
- **2020-01-23**: Freezed and lost samples because of heater issue in the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2), 11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2), 03/01/2020 (FB x2). Following samples could have been frozen, not sure: 06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB x2), 20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2), 11/10/2019 (FB x1), 11/10/2019  (durafet x1), 25/10/2019 (FB x2), 01/11/2019 (FB x1), 15/11/2019 (FB x1).

- **2020-01-15**: Results from 2019-04-19 to 2019-08-31 (sent in September 2019) were received. FB duplicates from 2019-08-09 were analysed as Durafet because of wrong box. One sample from 2019-06-07 (durafet) was analysed by Paris because of wrong box.
- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements. Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater. We will add a lack of DIC for this week. TA will be measured in Villefranche.
- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).
